External priors for the next generation of CMB experiments.

### 2016-02-25 Notes/CMBS4_priors_paper.tex
ready for submission

%==========
\begin{figure}[htbp]
\begin{center}
\includegraphics{{prior_omnuh2_lmin=4_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
\caption{Projected constraints on the sum of the neutrino masses (absolute on the left and relative on the right) from CMB-S4 and current BAO measurements as a function of priors on the other cosmological parameters. The {\it internal} (marginalized constraints from CMB-S4 and current BAO) constraints on each parameter are given as $\sigma_{\rm pipeline}$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
\label{fig:prior_omeganuh2-h}
\end{center}
\end{figure}
%==========
%==========

\begin{figure}[htbp]
\begin{center}
\includegraphics{{prior_omnuh2_notau_lmin=50_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
\caption{Same as Fig.~1, but with $l<50$ modes excluded from CMB-S4, instead coming from Planck. Note the importance of obtaining information on the optical depth $\tau$ if the low-$l$ modes are not measured accurately.}
\label{fig:prior-50}
\end{center}
\end{figure}
%==========

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics{{prior_massless_neutrinos_lmin=4_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
\caption{Constraints on $N_{\rm{eff}}$ (absolute on the left and and relative to its value on the right) as a function of priors on $\Omega _{b} h^{2}$, $\Omega _{c} h^{2}$ and $n_{s}$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
\label{fig:prior_neff}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics{{prior_w_hubble_lmin=4_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
\caption{Constraints on $w$ (absolute on the left and and relative to its value on the right) as a function of priors on $H_{0}$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
\label{fig:prior_w-h}
\end{center}
\end{figure}

>>>>

%==========
\begin{figure}[htbp]
\begin{center}
\includegraphics{prior_omnuh2_lmin4}
\caption{Projected constraints on the sum of the neutrino masses (absolute on the left and relative on the right) from CMB-S4 and current BAO measurements as a function of priors on the other cosmological parameters. The {\it internal} (marginalized constraints from CMB-S4 and current BAO) constraints on each parameter are given as $\sigma_{\rm pipeline}$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
\label{fig:prior_omeganuh2-h}
\end{center}
\end{figure}
%==========
%==========

\begin{figure}[htbp]
\begin{center}
\includegraphics{prior_omnuh2_l50}
\caption{Same as Fig.~1, but with $l<50$ modes excluded from CMB-S4, instead coming from Planck. Note the importance of obtaining information on the optical depth $\tau$ if the low-$l$ modes are not measured accurately.}
\label{fig:prior-50}
\end{center}
\end{figure}
%==========

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics{prior_massless_neutrinos}
\caption{Constraints on $N_{\rm{eff}}$ (absolute on the left and and relative to its value on the right) as a function of priors on $\Omega _{b} h^{2}$, $\Omega _{c} h^{2}$ and $n_{s}$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
\label{fig:prior_neff}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics{prior_w_hubble}
\caption{Constraints on $w$ (absolute on the left and and relative to its value on the right) as a function of priors on $H_{0}$. The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI.}
\label{fig:prior_w-h}
\end{center}
\end{figure}
